timesliced_random_cell_selection

### 2018-11-02 src/raster_sjl.Rmd
depth layer selection solved (see take 2 for code)

The next piece of data we need is the observation data itself. I've sent you the observations.csv in the email with this code.
```{r}
obs <- read.csv("../data/observations3.csv") #change this path to your .csv location
head(obs)
```
A note about obs$depth. This is not a measurement, but relates to the layer in the raster bricks. E.G. the observation in row one was found at rasbr[[15]], the observation in row 3 at rasbr[[17]]. I created this field myself.

@@

let's get the values manually
```{r}
test15 <- extract(x=rasbr_aea[[15]], y = obssp)
test22 <- extract(x=rasbr_aea[[22]], y = obssp)
test17 <- extract(x=rasbr_aea[[17]], y = obssp)
test17
```

@@

take 2
```{r}
Data_Loop <-NULL #Gonna put my loop data in here
for (i in 1:length(obssp)) {  # CYCLES THROUGH THE ROWS
  de <- obssp$depth[[i]]  #have a variable for the depth layer
  print(de)
  obssp$samtest <- extract(x=rasbr_aea[[de]], y = obssp) #this is the equation you will be calculating for every value of y

@@

>>>>

The next piece of data we need is the observation data itself. I've sent you the observations.csv in the email with this code.
```{r}
obs <- read.csv("../data/observations3.csv", header = TRUE) #change this path to your .csv location
head(obs)
```
A note about obs$depth. This is not a measurement, but relates to the layer in the raster bricks. E.G. the observation in row one was found at rasbr[[15]], the observation in row 3 at rasbr[[17]]. I created this field myself.

@@

let's get the values manually
```{r}
testrow1 <- read.csv("../data/row1.csv", header = TRUE)
testrow1xy <- testrow1[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow1sp <- SpatialPointsDataFrame(coords = testrow1xy, data = testrow1, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
testrow1sp
test15 <- extract(x=rasbr_aea[[15]], y = testrow1sp)
test15
testrow2 <- read.csv("../data/row1.csv", header = TRUE)
testrow2xy <- testrow2[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow2sp <- SpatialPointsDataFrame(coords = testrow2xy, data = testrow2, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
testrow2sp
test22 <- extract(x=rasbr_aea[[22]], y = testrow2sp)
test22
testrow3 <- read.csv("../data/row1.csv", header = TRUE)
testrow3xy <- testrow3[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow3sp <- SpatialPointsDataFrame(coords = testrow3xy, data = testrow3, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
testrow3sp
test17 <- extract(x=rasbr_aea[[17]], y = testrow3sp)
test17
```

row 1 (dpeth 15) should be 32.8761...
row 2 (depth 22) should be 33.10022...
row 3 (depth 17) should be 32.90343...

@@

take 2

```{r}
#Data_Loop <-NULL #Gonna put my loop data in here
for (i in 1:length(obssp)) {  # CYCLES THROUGH THE ROWS
  de <- obssp$depth[[i]]  #have a variable for the depth layer
  #print(de)
  obssp$samtest[i] <- extract(x=rasbr_aea[[de]], y = obssp) #this is the equation you will be calculating for every value of y

@@

  #print the i value so you can track progress. Good for longer loops
  print(i)
  #Close the loop
}
#Data_Loop
obssp$samtest
obssp
```

so with this code, the values are correct but I get the following error "number of items to replace is not a multiple of replacement length". I don't know why... but it works...

Ok next step, can you dynamically name the column with the variable in question (or at least the name of the original netcdf)
